### 2021-04-23 nih2/NIHGrant.tex
Some additions

% \usepackage[utf8]{inputenc} % Required for inputting international characters
% \usepackage[T1]{fontenc} % Output font encoding for international characters
% A note on fonts: As of 2019, NIH allows Arial, Georgia, Helvetica, and Palatino Linotype. Georgia and Arial are commercial fonts so you will need to use XeLaTeX and have them installed on your machine to use them. Palatino & Helvetica are available as free LaTeX packages so select the one you want and comment out the other.
\usepackage{palatino} % Palatino font
\linespread{1.05} % A little extra line spread is better for the Palatino font
%\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font

\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
\usepackage{graphicx} % Required for including images
\usepackage{booktabs} % Nice rules in tables
\usepackage{wrapfig} % Required for text to wrap around figures and tables
\usepackage[labelfont=bf]{caption} % Make figure numbering in captions bold
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry} % Page margins
\usepackage[style=numeric, sorting=nyt]{biblatex}
\pagestyle{empty} % Suppress headers and footers

@@

This is an example citation \cite{baraniukCompressiveSensingLecture2007}. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Praesent porttitor arcu luctus, imperdiet urna iaculis, mattis eros. Pellentesque iaculis odio vel nisl ullamcorper, nec faucibus ipsum molestie. Sed dictum nisl non aliquet porttitor. Etiam vulputate arcu dignissim, finibus sem et, viverra nisl. Aenean luctus congue massa, ut laoreet metus ornare in. Nunc fermentum nisi imperdiet lectus tincidunt vestibulum at ac elit. Nulla mattis nisl eu malesuada suscipit.

Aliquam arcu turpis, ultrices sed luctus ac, vehicula id metus. Morbi eu feugiat velit, et tempus augue. Proin ac mattis tortor. Donec tincidunt, ante rhoncus luctus semper, arcu lorem lobortis justo, nec convallis ante quam quis lectus. Aenean tincidunt sodales massa, et hendrerit tellus mattis ac. Sed non pretium nibh. Donec cursus maximus luctus. Vivamus lobortis eros et massa porta porttitor.

Fusce varius orci ac magna dapibus porttitor. In tempor leo a neque bibendum sollicitudin. Nulla pretium fermentum nisi, eget sodales magna facilisis eu. Praesent aliquet nulla ut bibendum lacinia. Donec vel mauris vulputate, commodo ligula ut, egestas orci. Suspendisse commodo odio sed hendrerit lobortis. Donec finibus eros erat, vel ornare enim mattis et. Donec finibus dolor quis dolor tempus consequat. Mauris fringilla dui id libero egestas, ut mattis neque ornare. Ut condimentum urna pharetra ipsum consequat, eu interdum elit cursus. Vivamus scelerisque tortor et nunc ultricies, id tincidunt libero pharetra. Aliquam eu imperdiet leo. Morbi a massa volutpat velit condimentum convallis et facilisis dolor.

\begin{description}
	\item[Aim 1: Really cool stuff.]{}
	\item{1.1. First sub-aim with more details}
	\item{1.2. Second sub-aim with more details.}  
\end{description}

\begin{description}
	\item[Aim 2: Really cool stuff.]{}
	\item{2.1. First sub-aim with more details.}
	\item{2.2. Second sub-aim with more details.}
\end{description}

\begin{description}
	\item[Aim 3: Really cool stuff.]{ }
	\item{3.1. First sub-aim with more details.}
	\item {3.2. Second sub-aim with more details.}
	\item{3.3. Third sub-aim with more details.}
\end{description}

In hac habitasse platea dictumst. Curabitur mattis elit sit amet justo luctus vestibulum. In hac habitasse platea dictumst. Pellentesque lobortis justo enim, a condimentum massa tempor eu. Ut quis nulla a quam pretium eleifend nec eu nisl. Nam cursus porttitor eros, sed luctus ligula convallis quis. Nam convallis, ligula in auctor euismod, ligula mauris fringilla tellus, et egestas mauris odio eget diam. Praesent sodales in ipsum eu dictum.

@@

\begin{description} % For subheadings within a section, this template uses the {description} environment, it is not obtrusively large like a \subsection; and facilitates a brief optional subtitle; and it will wrap around figures and tables; it also has a decent amount of whitespace above/below which is less than for a section heading
	\item[A.1. Instructions.]{Optional subtitle}
\end{description}

Explain the importance of the problem or critical barrier to progress in the field that the proposed project addresses.

Explain how the proposed project will improve scientific knowledge, technical capability, and/or clinical practice in one or more broad fields.

Describe how the concepts, methods, technologies, treatments, services, or preventative interventions that drive this field will be changed if the proposed aims are achieved.

\begin{description}
	\item[A.2. Subheading.]{}
\end{description}

@@

Current methods to determine cognitive representations of tinnitus
are inefficient and introduce bias, resulting in a lack of standardization in tinnitus assessment \cite{henryTinnitusEpidemiologicPerspective2020}.
Alternate forced-choice (AFC) paradigm tasks ask the patient to determine which of two sounds
is closer to their tinnitus percept \cite{henryComparisonTwoComputerautomated2001,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013,korthOneStepCloser2020}.
Recent computer and methodological advances have made the test more portable and efficient,
but the AFC paradigm still relies on assumptions about the subject's tinnitus percept.
Tinnitus percepts are too heterogeneous to be represented by pure tones or small-envelope waveforms.
Adequately sampling the psychoacoustic space of possible tinnitus percepts via an AFC task is unfeasible.
Other approaches have attempted to capture the richness of tinnitus percepts using likeness measures,
in which the subject rates whether a presented stimulus is part of their tinnitus percept or not \cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While this method is able to capture more features of cognitive representations of tinnitus,
it is time-consuming and limited by the aural skills of the subject \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
Both these approaches involve the subject comparing an external stimulus to their cognitive representation of the tinnitus percept,
however AFC tasks introduce biases by artificially limiting the stimulus space and likeness measures are time-consuming.

\emph{We believe that a novel reverse correlation-based approach will produce efficient and unbiased cognitive representations of tinnitus percepts}
\cite{gosselinSuperstitiousPerceptionsReveal2003}.
Reverse correlation allows for unconstrained and unbiased
characterization of latent representations directly from stimulus-response data by eliciting responses to
richly varying stimuli, such as white noise (Marmarelis \& Marmarelis, 1978; Nishimoto et al., 2006). Richstimuli, by virtue of the fact that they are inherently vague, force the top-down process to exert a clearly
measurable influence on responses. Latent representations that drive the top-down process can then be
estimated by regressing observed responses against the stimuli over many trials (Mineault et al., 2009).
Reverse correlation, as a method, is powerful enough to characterize any aspect of neurological,
cognitive or psychological function that can be modeled as a transductive process (Ringach, 2004). It has
become a primary method used to characterize the latent representations encapsulated in neural tuning
(e.g., receptive fields; Ringach, 2004), and is closely related to the widely-used “white noise approach” to
characterizing physiological (Marmarelis \& Marmarelis, 1978) and engineering (Ljung, 1999) systems.

@@

Referencing a table using it's label: Table \ref{tab:example}. Maecenas consectetur metus at tellus finibus condimentum. Proin arcu lectus, ultrices non tincidunt et, tincidunt ut quam. Integer luctus posuere est, non maximus ante dignissim quis. Nunc a cursus erat. Curabitur suscipit nibh in tincidunt sagittis. Nam malesuada vestibulum quam id gravida. Proin ut dapibus velit. Vestibulum eget quam quis ipsum semper convallis. Duis consectetur nibh ac diam dignissim, id condimentum enim dictum. Nam aliquet ligula eu magna pellentesque, nec sagittis leo lobortis. Aenean tincidunt dignissim egestas. Morbi efficitur risus ante, id tincidunt odio pulvinar vitae. Proin ut dapibus velit. Vestibulum eget quam quis ipsum semper convallis. Duis consectetur nibh ac diam dignissim, id condimentum enim dictum.

@@

Referencing a figure using it's label: Figure \ref{fig:example}. Proin lobortis efficitur dictum. Pellentesque vitae pharetra eros, quis dignissim magna. Sed tellus leo, semper non vestibulum vel, tincidunt eu mi. Aenean pretium ut velit sed facilisis. Ut placerat urna facilisis dolor suscipit vehicula. Ut ut auctor nunc. Nulla non massa eros. Proin rhoncus arcu odio, eu lobortis metus sollicitudin eu. Duis maximus ex dui, id bibendum diam dignissim id. Aliquam quis lorem lorem. Phasellus sagittis aliquet dolor, vulputate cursus dolor convallis vel. Suspendisse eu tellus feugiat, bibendum lectus quis, fermentum nunc. Nunc euismod condimentum magna nec bibendum. Curabitur elementum nibh eu sem cursus, eu aliquam leo rutrum. Sed bibendum augue sit amet pharetra ullamcorper. Aenean congue sit amet tortor vitae feugiat. Vestibulum vestibulum luctus metus venenatis facilisis. Suspendisse iaculis augue at vehicula ornare. Sed vel eros ut velit fermentum porttitor sed sed massa. Fusce venenatis, metus a rutrum sagittis, enim ex maximus velit, id semper nisi velit eu purus.

@@

\begin{description}
	\item[B.1. Instructions.]{}
\end{description}

Explain how the application challenges and seeks to shift current research or clinical practice paradigms.

Describe any novel theoretical concepts, approaches or methodologies, instrumentation or interventions to be developed or used, and any advantage over existing methodologies, instrumentation, or interventions.

Explain any refinements, improvements, or new applications of theoretical concepts, approaches or methodologies, instrumentation, or interventions.

@@

\begin{description}
	\item[C.1. Instructions.]{}
\end{description}

Describe the overall strategy, methodology, and analyses to be used to accomplish the specific aims of the project. Unless addressed separately in Item 15 (Resource Sharing Plan), include how the data will be collected, analyzed, and interpreted as well as any resource sharing plans as appropriate.

Discuss potential problems, alternative strategies, and benchmarks for success anticipated to achieve the aims.

If the project is in the early stages of development, describe any strategy to establish feasibility, and address the management of any high risk aspects of the proposed work.

Point out any procedures, situations, or materials that may be hazardous to personnel and precautions to be exercised. A full discussion on the use of Select Agents should appear in Item 11, below.

As applicable, also include the following information as part of the Research Strategy, keeping within the three sections listed above: Significance, Innovation, and Approach.

\begin{description}
	\item[C.2. Preliminary Studies for New Applications]{}
\end{description}

Preliminary Studies for New Applications: For new applications, include information on Preliminary Studies. Discuss the PD/PI's preliminary studies, data, and or experience pertinent to this application. Except for Exploratory/Developmental Grants (R21/R33), Small Research Grants (R03), and Academic Research Enhancement Award (AREA) Grants (R15), preliminary data can be an essential part of a research grant application and help to establish the likelihood of success of the proposed project. Early Stage Investigators should include preliminary data (however, for R01 applications, reviewers will be instructed to place less emphasis on the preliminary data in application from Early Stage Investigators than on the preliminary data in applications from more established investigators).

>>>>

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
% A note on fonts: As of 2019, NIH allows Arial, Georgia, Helvetica, and Palatino Linotype. Georgia and Arial are commercial fonts so you will need to use XeLaTeX and have them installed on your machine to use them. Palatino & Helvetica are available as free LaTeX packages so select the one you want and comment out the other.
\usepackage{palatino} % Palatino font
\linespread{1.05} % A little extra line spread is better for the Palatino font
% \usepackage{helvet} % Helvetica font
% \renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font

\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
\usepackage{graphicx} % Required for including images
\usepackage{booktabs} % Nice rules in tables
\usepackage{wrapfig} % Required for text to wrap around figures and tables
\usepackage[labelfont=bf]{caption} % Make figure numbering in captions bold
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry} % Page margins
\usepackage[style=numeric, sorting=nyt]{biblatex}
\addbibresource[]{mybib.bib}
\pagestyle{empty} % Suppress headers and footers

@@

The \textbf{objective} of this proposal is to directly and more completely characterize the perceptual experience of tinnitus using the novel application of a primary method for uncovering latent perceptual representations: reverse correlation.
Tinnitus is the perception of ringing, buzzing, or hissing in the ears, which can range from mild and transient to debilitating.
In the U.S. alone, it affects 45 million people per year, 30\% of which report their tinnitus to be moderate to severe.
A primary form of treatment habituation therapy that retrains a patient’s nervous system by habituating it to external sounds that mimic the perceptual experience of the tinnitus sound.
Habituation therapies require accurate estimates of patients’ tinnitus experience in order to promote patient outcomes.
There is a pressing need for new approaches to uncovering individuals’ perceptual experience of tinnitus, because current estimation methods rely on strongly reductionist assumptions concerning the nature of tinnitus sounds, and produce results that are correspondingly biased and incomplete. Reverse correlation holds promise in this regard, as a primary method used to characterize neural tuning that is known to allow for unconstrained and unbiased estimation of latent neural representations (e.g., neural receptive fields [17]), as well as higher-level cognitive representations, including psychophysical kernels that drive the top-down processes of perception (e.g., face or phoneme recognition)[1,5,14,18], and even abstract psychological categories (e.g., “male” vs. “female” faces)[4,10,16], all on the basis of fairly simple stimulus-response data [11,15]. Despite its wide acceptance in other areas of inquiry, reverse correlation has not been brought to bear with respect to uncovering tinnitus experience.

Our \textbf{long-term goal} is to directly uncover and more completely characterize the perceptual experience of tinnitus using the demonstrated capabilities of the reverse correlation approach.
Our guiding hypothesis is that reverse correlation will produce estimates of tinnitus percepts that are substantially more rich, individualized and unbiased than currently possible using existing approaches. The rationale is that high quality characterization of tinnitus percepts can promote detailed assessment of tinnitus, helping to explain individual variability in tinnitus experience, and ultimately informing individualized treatment through enhanced habituation therapies. The proposed work will simultaneously improve the efficiency of the reverse correlation method itself, further enhancing its potential for adoption in clinical settings. We will test our central hypothesis and attain our objective via the following specific aims:

\begin{description}
	\item[Aim \#1: Uncover and reconstruct cognitive representations of tinnitus]{} 
\end{description}

Participants will classify white noise stimuli as sounding like their tinnitus or not.
We will use reverse correlation to infer an unbiased estimate of each participant's cognitive representation of their tinnitus percept.

\begin{description}
	\item[Aim \#2: Develop efficient reconstruction algorithm for cognitive representations using compressive sensing]{} 
\end{description}

The efficiency of this method can be optimized to require fewer samples using advanced signal processing techniques.
We will develop an open-source compressive sensing data analysis pipeline to acquire convergent cognitive representations using fewer trials.
Our pilot data demonstrates that compressive sensing affords a 90\% decrease in number of trials for equivalent resulant latent representation.
We will also develop and distribute an open-source software implementation the of the reverse correlation method for speech perception,
including the proposed compressive sensing framework, for use by the research community.

\begin{description}
	\item[Aim \#3: Characterize and interpret cognitive representations of tinnitus]{} 
\end{description}

Our compressive sensing framework will allow for rapid data acquisition from participants.
We will characterize cognitive representations of tinnitus between participants and over time.
What is the space of tinnitus cognitive representations?
Are there subtypes or clusters on a lower dimensional manifold?
We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
providing direct insight into commonalities and variability of tinnitus experience in and between subjects.

@@

@@

Current methods to determine cognitive representations of tinnitus
are inefficient and introduce bias, resulting in a lack of standardization in tinnitus assessment \cite{henryTinnitusEpidemiologicPerspective2020}.
Alternate forced-choice (AFC) paradigm tasks ask the patient to determine which of two sounds
is closer to their tinnitus percept
\cite{henryComparisonTwoComputerautomated2001,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013,korthOneStepCloser2020}.
Recent computer and methodological advances have made the test more portable and efficient,
but the AFC paradigm still relies on assumptions about the subject's tinnitus percept.
Tinnitus percepts are too heterogeneous to be represented by pure tones or small-envelope waveforms.
Adequately sampling the psychoacoustic space of possible tinnitus percepts via an AFC task is unfeasible.
Other approaches have attempted to capture the richness of tinnitus percepts using likeness measures,
in which the subject rates whether a presented stimulus is part of their tinnitus percept or not \cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While this method is able to capture more features of cognitive representations of tinnitus,
it is time-consuming and limited by the aural skills of the subject \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
Both these approaches involve the subject comparing an external stimulus to their cognitive representation of the tinnitus percept,
however AFC tasks introduce biases by artificially limiting the stimulus space and likeness measures are time-consuming.
\emph{We believe that a novel reverse correlation-based approach will produce efficient and unbiased cognitive representations of tinnitus percepts}
\cite{gosselinSuperstitiousPerceptionsReveal2003}.

Reverse correlation allows for unconstrained and unbiased
characterization of latent representations directly from stimulus-response data by eliciting responses to
richly varying stimuli, such as white noise (Marmarelis \& Marmarelis, 1978; Nishimoto et al., 2006).
Rich stimuli, by virtue of the fact that they are inherently vague, force the top-down process to exert a clearly
measurable influence on responses. Latent representations that drive the top-down process can then be
estimated by regressing observed responses against the stimuli over many trials (Mineault et al., 2009).
Reverse correlation, as a method, is powerful enough to characterize any aspect of neurological,
cognitive or psychological function that can be modeled as a transductive process (Ringach, 2004). It has
become a primary method used to characterize the latent representations encapsulated in neural tuning
(e.g., receptive fields; Ringach, 2004), and is closely related to the widely-used “white noise approach” to
characterizing physiological (Marmarelis \& Marmarelis, 1978) and engineering (Ljung, 1999) systems.

@@

Referencing a table using its label: Table \ref{tab:example}. Maecenas consectetur metus at tellus finibus condimentum. Proin arcu lectus, ultrices non tincidunt et, tincidunt ut quam. Integer luctus posuere est, non maximus ante dignissim quis. Nunc a cursus erat. Curabitur suscipit nibh in tincidunt sagittis. Nam malesuada vestibulum quam id gravida. Proin ut dapibus velit. Vestibulum eget quam quis ipsum semper convallis. Duis consectetur nibh ac diam dignissim, id condimentum enim dictum. Nam aliquet ligula eu magna pellentesque, nec sagittis leo lobortis. Aenean tincidunt dignissim egestas. Morbi efficitur risus ante, id tincidunt odio pulvinar vitae. Proin ut dapibus velit. Vestibulum eget quam quis ipsum semper convallis. Duis consectetur nibh ac diam dignissim, id condimentum enim dictum.

@@

Referencing a figure using its label: Figure \ref{fig:example}. Proin lobortis efficitur dictum. Pellentesque vitae pharetra eros, quis dignissim magna. Sed tellus leo, semper non vestibulum vel, tincidunt eu mi. Aenean pretium ut velit sed facilisis. Ut placerat urna facilisis dolor suscipit vehicula. Ut ut auctor nunc. Nulla non massa eros. Proin rhoncus arcu odio, eu lobortis metus sollicitudin eu. Duis maximus ex dui, id bibendum diam dignissim id. Aliquam quis lorem lorem. Phasellus sagittis aliquet dolor, vulputate cursus dolor convallis vel. Suspendisse eu tellus feugiat, bibendum lectus quis, fermentum nunc. Nunc euismod condimentum magna nec bibendum. Curabitur elementum nibh eu sem cursus, eu aliquam leo rutrum. Sed bibendum augue sit amet pharetra ullamcorper. Aenean congue sit amet tortor vitae feugiat. Vestibulum vestibulum luctus metus venenatis facilisis. Suspendisse iaculis augue at vehicula ornare. Sed vel eros ut velit fermentum porttitor sed sed massa. Fusce venenatis, metus a rutrum sagittis, enim ex maximus velit, id semper nisi velit eu purus.

@@

The proposed project is innovative for several reasons.
First, we will leverage interdisciplinary collaboration between engineering (Lammert)
and hearing science (Ben) to characterize tinnitus to inform clinical care.
Second, we will apply reverse correlation to the tinnitus domain in a novel application,
which promises to deliver unbiased, high-dimensional estimates of cognitive representations of tinnitus.
Third, we will develop a signal processing pipeline to leverage compressive sensing
to acquire accurate estimates of cognitive representations of tinnitus using significantly fewer samples.
This pipeline will save experimenters and subjects time and will enable researchers
to collect data from more subjects and from individual subjects over time.
We will release our open-source software tool online with bindings to popular scientific computing languages.

@@

In the proposed project, we will use reverse correlation to reveal unbiased high-dimensional
representations of tinnitus and further characterize the condition
using dimensionality-reduction and density-based clustering.
In \emph{Aim \#1}, we will develop and run an experimental paradigm
in which tinnitus patients listen to noisy stimuli and perform an alternate forced-choice task
answering the question, ``Does this sound like your tinnitus?''
In \emph{Aim \#2},
